Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-18 Ben_Manuscripts/structure_paper/response_to_reviewers.tex

    \item \begin{quote} \textit{This manuscript describes atomistic molecular
	    dynamics simulations and diffraction analysis of hexagonally-arranged pores,
	    each of which is made of many columns of the monomer Na-GA3C11. This physical
	    system is of interest because such nanopores have potential to transform
	    filtration applications. This work is of potential interest to the JPC
	    readership because it provides atomistic insight into the origins of
	    diffraction reflections observed in experiments, which could be used to resolve
	    discrepancies about what the structure of these hexagonal arrays are, or used
	    to engineer better filters. Overall, the manuscript provides comprehensive
	    descriptions of metrics used to evaluate the simulated structures against
	    experiments, but the number of things described and length of these
	    descriptions obscures whether significant new physical insight into this system
	    is made.} 
    \end{quote}

    Author reply: We thank the reviewer for their constructive feedback and aim to address all of their concerns.

    \item \begin{quote}
    \textit{As written, it is not clear if the authors are presenting this
	    study as a validation of GAFF and the present equilibration techniques, or
	    whether this study is providing significant new physical insight into these
	    lyotropic liquid crystals. The paper reads a bit more like the former, with a
	    comprehensive discussion of the degree to which five scattering features
	    expected in experiments are predicted in simulations. However, at the same
	    time, the authors make arguments including (1) pores are made from five columns
	    of monomers, (2) that water is present in the "dry" structures, and (3) that a
	    scattering feature comes from tail packing, not tilt: These observations
	    *could* be new physical insight into lyotropic liquid crystal structure, but as
	    presented seem more like hypotheses than conclusions:}

    Author reply: We thank the reviewer for offering their interpretation
    of the purpose of our study, as it is important that we properly convey our
    message. The main purpose our work is to give a detailed description of the
    structure of a lyotropic liquid crystal membrane backed by experimental data.
    This work lays a foundation for future transport studies. By matching 2D-WAXS
    data, we have attempted to unveil the most experimentally-consistent structure
    possible. This is unlikely to be achieved if one assembled these systems using
    united atom or coarse grained models due to the large number of potential
    metastable configurational basins which plague a system like ours which exhibts
    such slow dynamics.

    We do not intend for this study to be a validation of GAFF for this
    particular system. We believe we would come to similar conclusions using other
    force fields, however validation of this hypothesis is left for a future study.
    We chose GAFF because it is widely used to simulate organic molecules and there
    are no force fields specifically built for our system. We are interested in
    what information we can gain from an out-of-the-box force field and in future
    work, we will validate whether GAFF is sufficient for reproducing trends in
    experimental separation properties. Since our ultimate goal is to design new
    monomers for solute-specific separations, we will be employing the same 
    techniques used in this work to unsynthesized monomers. In most cases, we will
    not have an experimental dataset to use for comparison. Despite all of the 
    structural intracacies which we have revealed in this study, one of our main
    conclusions is that regardless of which system we study, the radial distribution
    of monomer components stays consistent. From this, we can hypothesize that 
    we will extract similar transport results regardless of which configuration
    we use to conduct transport studies. This is an extremely important finding
    which may have been undersold in the original draft of the manuscript.

### 2018-11-18 Ben_Manuscripts/structure_paper/Final_Draft.tex
Updates

@@

  Previous literature has attributed the R-spots reflection in this particular
  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
  This explanation is not unfounded as there are examples in literature of
  systems where tilted liquid crystals give rise to reflections that resemble
  R-spots (Cite, Cite). We measured the tilt angle of the alkane chains of the
  280 K system by measuring the angle made by the vector extending from top to
  bottom of each tail with respect to the membrane plane. We found that it
  equilibrates to an average tilt angle of -2 $\pm$
  13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Even when we placed position restraints on the
  monomers in a tilted initial configuration, monomers quickly reduced their tilt
  relative to the $xy$ plane to an angle statisically indistinguishable from zero
  (see Section \ref{S-section:tail_tilt} of the SI). While it is plausible that 
  our forcefield may in part be responsible for the tendency of monomers to stay
  nearly flat, the monomer tails lack the functional groups which are known to
  facilitate tail tilting.

>>>>

  % reworking paragraph
  A molecular-level understanding of LLC polymer membrane structure, enabled by
  molecular dynamics (MD) simulations, will enhance our understanding of the role
  of monomer structure in solute transport and provide guidelines to reduce the
  large chemical space available to design monomers for creation of
  separation-specific membranes. It is important that we model the system with
  a nanoscopic pore structure that is maximally consistent with experimental
  data.

@@

  Previous literature has attributed the R-spots reflection in this particular
  WAXS dataset as the result of tilted alkane chains~\cite{feng_scalable_2014}.
  This explanation is not unfounded as there are examples in literature of
  systems where tilted liquid crystals give rise to reflections that resemble
  R-spots (Cite, Cite). We measured the tilt angle of the alkane chains of the
  280 K system by measuring the angle made by the vector extending from top to
  bottom of each tail with respect to the membrane plane. We found that it
  equilibrates to an average tilt angle of -2 $\pm$
  13\degree~(Figure~\ref{fig:tilt}), far from the 37\degree~tilt angle previously
  used to explain R-spots. Even when we placed position restraints on the
  monomers in a tilted initial configuration, monomers quickly reduced their tilt
  relative to the $xy$ plane to an angle statisically indistinguishable from zero
  (see Section \ref{S-section:tail_tilt} of the SI). While it is plausible that 
  our force field may in part be responsible for the tendency of monomers to stay
  nearly flat, the monomer tails lack the functional groups which are known to
  facilitate tail tilting.
